Self-reported LLM usage and results on a data science project: Evidence from a Canadian undergraduate data science course

### 2024-08-12 paper/paper.qmd
Updated first paragraph of introduction

There are many aspects of trustworthy data science, including education, culture, and workflow to name a few. One aspect of special importance is the tools that we use to do data science: the computers, programming languages, and environments among other factors. The wide release of user-friendly Large Language Models (LLMs), particularly OpenAI's ChatGPT, is the rare instance of a new tool being added to the data science toolkit.

>>>>

Trustworthy data science is the practice of conducting data analysis in a transparent, ethical, and reliable manner. These principles are reflected in various ways, through education, culture, and workflow.  To stay current, data scientists must continually update their knowledge of best practices for transparency and reproducibility, foster a culture which values different perspectives and accountability, and critically think about the broader impact of data-driven decisions.  The wide release of user-friendly Large Language Models (LLMs), particularly OpenAI’s ChatGPT, has transformed the data science toolkit, offering powerful tools for natural language processing and generation, thus enhancing aspects of data analysis and automation.
